Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal distribution

### 2018-05-21 manuscript.tex
Add files via upload

In this Section, we perform a bootstrap analysis to measure the standard errors associated to SN mean RV, SN median RV, RV, FWHM, SN FWHM, BIS SPAN and $\gamma$. Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other. Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Gaussian distribution scaled to the error of each given point. To bypass this problem, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF. We then fit a Normal or a SN to each of these CCFs and then calculate the standard deviations of the distribution for the location parameters (RV, SN mean RV or SN median RV), the width parameters (FWHM or SN FWHM) and the parameters of asymmetry (BIS SPAN or $\gamma$).
\comment{It is not clear what you are doing here. I can understand bootstrapping a time series: you shuffle all the values keeping the time stamps fixed. How do you bootstrap a stellar spectrum? Do you shuffle the intensity values keeping the wavelengths fixed? That would produce a mess. Do you just add different levels of random noise? But the spectra already have noise in them, they are real observations. You need to state more clearly here what you did.}

>>>>

In this Section, we perform a bootstrap analysis \citep{davison1997bootstrap, efron1994introduction} in order to retrieve the standard errors associated to SN mean RV, SN median RV, RV, FWHM, SN FWHM, BIS SPAN and $\gamma$. Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other. Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Gaussian distribution scaled to the error of each given point. A detailed discussions of the methods nowadays available to resampling in situations with dependent data structures is available in \citep{lahiri2013resampling}. All the bootstrap methods that deal with dependant data structures rely on the so called Block Bootstrap methods, originally introduced by \citep{wilks1997resampling}. In our particular case, since each point in a CCF is correlated with each other, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF. We then fit a Normal or a SN to each of these CCFs and then calculate the standard deviations of the distribution for the location parameters (RV, SN mean RV or SN median RV), the width parameters (FWHM or SN FWHM) and the parameters of asymmetry (BIS SPAN or $\gamma$).
